\LARGE \bf Enriching Robot's Actions with Affective Movements

### 2017-06-11 RO-MAN-2017-2/Parts/description.tex
Reviewed

The description files allow the parametrization and extent the system to fit other applications is required. To standarize the mechanisms to describe these files, it was decided to create a language to describe them. This allows other researchers to create their own files and to extend the language to fit their needs. It was decided to use the Extended Backus-Naur Form (EBNF) to describe this language.
\subsection{Emotion Description} 
The language created to describe emotion descriptors is the following:
\begin{small}

>>>>

Description files allow the parametrization and extention of the system to fit other applications. A language was created to define the content of these files. This allows other researchers to create their own files and to extend the language to fit their needs. The Extended Backus-Naur Form (EBNF) that describes this language is reported below.
\subsection{Emotion Description} 
The language created to describe emotion descriptors is the following:
\begin{small}
